---
title: "FAIRS report, Round 2"
author: "created by: Dorothy V. M. Bishop"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: 
    reference_docx: word-styles-reference-01.docx
  html_document: null
---

<!---  NB confidential files are on the external ExtremePro drive -->

<!---  Use with masterloop.R to create multiple personal versions -->

<!---  Added some changes to double check report ordering matches -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(viridis)
require(here)
require(janitor)
require(tidyr)
library(stringr)
require(flextable)
#require(explore) #not needed but helps to visualise data


```
<!--- https://rmarkdown.rstudio.com/articles_docx.html for page numbers-->



```{r setupdata, echo=F}
#thisrow <- 1 #set to zero if no individualised data in report. Otherwise thisnumber specifies the row to be used in individualsed report
thisrow <- 0
#NEED THE UNCODED CSV

#for testing: wanted file is just top file in list for nwo
#myf<-list.files()  #all files in working directory
#this is myf[1] in test, but spell it out here
set.seed(1) #for reproducible randomisation
thisf <- "round2/Round2_final_redacted.csv"
#thisf <- "round2/cm6gca0fd0099la08aoef5eq6-analytics-uncoded-08-02-2025.csv"

df <- read.csv(thisf)
myjisc <- read.csv('round2/R2_survey_template.csv')
mypanel <- read.csv('round2/From_MS_Forms copy.csv')
reportorder <- read.csv('reportOrder_round2.csv') #this should be blank file to start with, just with headers - we add to it with each created report
signedup <- 97 #this is all from Round 1 plus 2 extras

#THIS WILL CREATE ORDERED NUMBERED REPORTS
myf<-list.files(pattern="report")
thisrow<-length(myf)+1
##############

#OR SPECIFY ROW HERE: ZERO FOR GENERIC
thisrow <- 0 #For generic report set to zero

thispanel<-df[,2] #retain only those who completed the survey
w<-which(mypanel$anonid %in% thispanel)
mypanel<-mypanel[w,]
#NB mypanel will be in a different order, but we are only using mypanel to report demographics in table format, not for individuals, so this is OK

jisccodes <- seq(3,37,2) #X Codes in JISC file corresponding to items

#because of large N anaesthetists we coded them separately;

names(df)<-substring(names(df),1,12) #shorten df names to 12 chars
names(df)[2]<-'ID'

#df<-df[,-3]  # remove item that is just agreeing to take part.(Has been resaved since doing that, so now obsolete code)
df<-clean_names(df)

ncases <- nrow(df)
#df[1:ncases,1]<-NA

#rename col for group
w<-which(names(df)=="x3_please_s")
names(df)[w]<-'group'
df$group<-as.factor(df$group)
levels(df$group)<-c('1_S','2_R','3_O')


#df<-df[order(df$group),] #order by group - easier to follow when listing free text responses



```

## Summary of FAIRS Survey, round 2

### Personalised report: `r df[thisrow,1]`

`r reportorder<-rbind(reportorder,df[thisrow,1:3])`
This is a report to provide feedback to participants in Round 2 of the FAIRS survey.  For background to the survey, please see the protocol here: <https://osf.io/mzjsh/>.  


```{r numformat,echo=F}
#Format numbers so they have same n decimal places, even if zero at end
#This returns a string

numformat=function(mynum,ndecimals){
#NB this is applied to a vector of numbers
  newnum <- format(round(mynum,ndecimals),nsmall=ndecimals)
  w<-which(newnum=='100.0')
  if(length(w)>0){
  newnum[w]<-'100'}
  
  return(newnum)
}

```

```{r gatherfreetext, echo=F}
#modifications to numbering
#Item number is first digit, then group, then seq random number
gatherfree <- function(myitem,mytext){
 #First shuffle order
  randnums<-sample(1:length(mytext))

  #create prefix
  mytextc1<-paste0(myitem,"_",substr(df$group[randnums],3,3),"_")

  mytextc2<-mytext[randnums]  #and for text
  myo<-order(mytextc1,decreasing=TRUE)  #re-sort to keep all the groups together, group S first
  mytextc1<-mytextc1[myo]
  mytextc2<-mytextc2[myo]
  mykeep <- which(nchar(mytextc2)>1)

  mytextcd <- paste0(mytextc1[mykeep],1:length(mykeep),") ",mytextc2[mykeep])
  
  myft<-as.data.frame(mytextcd)

names(myft)<-'Free text'
# knitr::kable(mytext,escape=FALSE)
  set_flextable_defaults(font.size = 9)
myft <- flextable(as.data.frame(myft))
myft <- set_table_properties(myft,layout="autofit")
myft

}

```




`r signedup` panelists signed up to take part in the survey, and completed surveys were received from `r nrow(df)` of them.  An item was added at the end of the survey, as follows:
"We anticipate that patterns of responses may be different for those who are primarily involved in raising concerns about serious research misconduct (e.g. sleuths, whistleblowers, victims of research fraud) and those whose job it is to respond to reports of such concerns (e.g. research integrity officers). Could you please specify here which of those groups you identify with most strongly - or whether neither applies to you." The distribution of respondents was as follows: 
  
- Sleuths, Whistleblowers, etc (Group 1_S), N = `r length(which(df$group=='1_S'))`   
- Research Integrity Officers, etc (Group 2_R), N = `r length(which(df$group=='2_R'))`   
- Others (Group 3_O), N = `r length(which(df$group=='3_O'))`.  

Those responding Other were given the option to give more description of their background, and responded as follows:

**Further details of those in 'other' group**  
`r mytext <- df$x4_if_you_r; gatherfree(0, mytext)`
   
     
     

```{r analysepanel,echo=F}
mypanel<-clean_names(mypanel)
gtab <- as.data.frame(table(mypanel$gender))
names(gtab)<-c('Gender','N')
ctab <- as.data.frame(table(mypanel$which_continent_are_you_based_in))
names(ctab)<-c('Continent','N')
rtab <- table(mypanel$reason_for_interest_in_taking_part)

emails<-mypanel$email_address
nUK <- length(grep(".uk",emails))
edoms <- str_split(emails,"@")
edoms <- unlist(edoms)
edoms <- edoms[seq(2,length(edoms),2)]

countrylist<-vector()
for (e in 1:length(edoms)){
g <- as.integer(regexpr("\\.[^\\.]*$", edoms[e])) #position of final 
ecountry <- substr(edoms[e],(g+1),nchar(edoms[e]))
countrylist<-c(countrylist,ecountry)
}
countrylist<-tolower(countrylist)

```


```{r makecattab, echo=F} 
#tabular output for single option items
makecattab <- function(myjisc,itemnum,df,thisrow,myterms,jisccodes){
    itemcode<-paste0('x',jisccodes[itemnum],'_')
    w<- grep(itemcode,names(df))
    if(length(w)>1) {w <- w[-1]} #for these items, w should already be 1;
    
    #now recode items, using the myterms variable
    
    thist <-0
    for (t in 1:length(myterms)){
      x <- grep(myterms[t],df[,w]) #rows where this term matches
      df[x,w]<-t
      if(thisrow %in% x) {thist <-t}
    }
    
    
    rawtab <- table(df[,w],df$group)
    rawdf<-as.data.frame.matrix(rawtab)
    rawdf$All<-rowSums(rawdf[,1:3])
  
    sumtab <-as.data.frame.matrix(100*prop.table(as.matrix(rawdf),2))
    sumtab <- numformat(sumtab,1)
    Options <- unlist(as.vector(myjisc[itemnum,(7+(1:nrow(sumtab)))]))
    Options <- paste0(LETTERS[1:nrow(sumtab)],") ",Options)
    sumtab<-cbind(Options,sumtab)
    sumtab[thist,1]<-paste("*",sumtab[thist,1])

  
  myft <- flextable(as.data.frame(sumtab))
  if(thisrow==0){
  myft <- addhighlight(myft)
  }
  
myft <- set_table_properties(myft,layout="autofit")
myft
}
```

```{r myhighlight, echo=F}
addhighlight <- function(myft){
  cutoff1 <- 70 #setting cutoff dynamically doesn't work for some reason, so they are hard coded below
  cutoff2 <- 50
  color4 <- 'red'
  color3 <-'pink'
  color2 <- 'lightblue'
  color1 <- 'cornflowerblue'

#This miscodes any row with 100 in it.  I think this has to do with values being text rather than numeric, (for formatting purposes) but various attempts to fix it have failed.  

  myft <- highlight(myft, j = 2, i = ~ `1_S` > 49.999, color = color2)
    myft <- highlight(myft, j = 2, i = ~ `1_S` > 70.0, color = color1)
  myft <- highlight(myft, j = 2, i = ~ `1_S` < 50.0, color = color3)
  myft <- highlight(myft, j = 2, i = ~ `1_S` < 30.0, color = color4)


  myft <- highlight(myft, j = 3, i = ~ `2_R` > 49.999, color = color2)
    myft <- highlight(myft, j = 3, i = ~ `2_R` > 70.0, color = color1)
  myft <- highlight(myft, j = 3, i = ~ `2_R` < 50.0, color = color3)
  myft <- highlight(myft, j = 3, i = ~ `2_R` < 30.0, color = color4)
  
  
  
    myft <- highlight(myft, j = 4, i = ~ `3_O` > 49.999, color = color2)
      myft <- highlight(myft, j = 4, i = ~ `3_O` > 70.0, color = color1)
  myft <- highlight(myft, j = 4, i = ~ `3_O` < 50.0, color = color3)
  myft <- highlight(myft, j = 4, i = ~ `3_O` < 30.0, color = color4)
 
    myft <- highlight(myft, j = 5, i = ~ All > 49.999, color = color2)
  myft <- highlight(myft, j = 5, i = ~ All > 70.0, color = color1)
  myft <- highlight(myft, j = 5, i = ~ All < 50.0, color = color3)
  myft <- highlight(myft, j = 5, i = ~ All < 30.0, color = color4)

return(myft)
} 
```

```{r percentageagree, echo = FALSE}
#thisrow is 0 for generic report; otherwise specifies the panellist
propagree <- function(itemnum,df,cutoff,respmax,thisrow,jisccodes){ 

    itemcode<-paste0('x',jisccodes[itemnum],'_')
    w<- grep(itemcode,names(df))
    if(length(w)>1) {w <- w[-1]} #for these items, w should already be 1;
    
 
      if(length(w)==1){
      forrecode<-df[,w]
      oldvals<-c('Strongly agree','Moderately agree','Neither agree nor disagree','Moderately disagree','Strongly disagree')
      if(itemnum==11){
              oldvals<-c('Strongly agree','Agree','Neutral','Disagree','Strongly disagree')
      }
      newvals<-5:1
      df[,w]<-newvals[match(forrecode,oldvals)]  
      }
      
    thisbit <- as.data.frame(df[,w])
    
    agreetab<-data.frame(matrix (NA, nrow=length(w),ncol=6))
    names(agreetab)<-c('Subitem',levels(df$group),'All','Your response')
    myoptions <- 1:respmax

    #Check for 5 point scale and collapse extremes, so scale is now 1, 3, 5
    if(respmax==5){
      myoptions <-c(1.5,3,4.5)
      for(v in 1:length(w)){
        ww<-which(thisbit[,v]==4)
        thisbit[ww,v] <- 5   
        ww<-which(thisbit[,v]==2)
        thisbit[ww,v] <- 1 
      }
    }
   
    
    for (v in 1:length(w)){ #stepping through subitems
      thistab <- table(thisbit[,v],df$group)
      thistab <- cbind(thistab,table(thisbit[,v])) #last col has All cases
      ptab <- prop.table(thistab,2) #percentage of each response by group (2nd num indicates col percentage rather than row)
   
    agreetab[v,2:5]<-numformat(100*ptab[nrow(ptab),],1)

    agreetab[v,1]<-paste0(LETTERS[v],") ",myjisc[itemnum,(7+v)])
    if(thisrow>0){
      agreetab[v,6]<-df[thisrow,w[v]]
    }
    }

    
    if(thisrow==0){agreetab<-agreetab[,1:5]} #no column for individual response
     if(nrow(agreetab)==1){
       agreetab[1,1]<-'Moderately/strongly agree'
     }
    myft <- flextable(as.data.frame(agreetab))
    if(thisrow==0){
    myft <- addhighlight(myft) #Colour coding just for base report
    #This is in part because of glitch when response is 100% that makes the colours go wrong
    }
    myft <- set_table_properties(myft,layout="autofit")
    myft
}
```


The gender distribution was as follows:  
`r flextable(gtab)|> autofit()`    




The bulk of respondents were from Europe or N America:  
`r flextable(ctab) |> autofit()`    

<!--- And the distribution of email domains was as follows:  
`r knitr::kable(table(countrylist))`  --->

For each item, responses are shown by subgroup, where 1 = S(leuths), 2 = R(esearch Integrity Officers) and 3 = O(ther).  For simple multiple choice items, the table shows percentages in each group with a given response.   
In addition, for items with several subitems, the percentage with agreement/strong agreement is shown for each subitem.  

In Round 2, illustrative free text comments from Round 1 were selected to provide context for respondents. To see these and the full text of the Round 2 survey, please follow this link: https://osf.io/k9maf. 

Additional free text comments by panel members from Round 2 are included in this report.  these include a letter denoting the subgroup of the respondent, but the associated numerical codes are randomised for each item, so the number doesnot correspond to a specific individual.  

N.B. Each panel member receives an individualised version of this report that either includes a column showing which response they gave, or has * denoting their selection, depending on the item type. 


\pagebreak



## Burdens of serious research misconduct 
### Item 2: How common is the problem of serious research misconduct? 
Table shows percentages selecting each option in each group. NB For this item, the options are mutually exclusive. 
<!--To make it easier to detect agreement/disagreement, values above 70% have red background, and those below 50% have a grey background.  

NB!!! FOR SOME REASON THIS DOESN'T WORK IF THE ROW HAS A VALUE OF 100% IN IT. THESE NEED MANUALLY CORRECTING.-->


(For personalised reports, * denotes your response).

<!-- - A. Serious research misconduct is rare relative to the amount of published research literature 
- B. Serious research misconduct is becoming more prevalent and starting to pose a threat to the research literature 
- C. Serious research misconduct is already common enough to pose a major threat to the research literature -->



`r makecattab(myjisc,2,df,thisrow,c('rare','prevalent','common'),jisccodes)`
  

**Free text comments on item 2**    

`r mytext <- df$x6_2b_opt; gatherfree(2,mytext)` 

### Item 3: How harmful are the impacts of serious research misconduct to different segments of society? 
Please code as 1 (low harm) to 5 (strong harm).  
*For items using 5-point scale, the summary table shows the percentage selecting option 4 or 5.*  


`r  propagree(3,df,mycutoff,respmax=5,thisrow,jisccodes)`  
<!-- for those on 1-5 scale, can combine outer categories -->

**Free text comments on item 3**    

`r mytext <- df$x8_3b_opt; gatherfree(3,mytext)` 

## Goals of those responding to serious research misconduct 
### Item 4: In responding to serious research misconduct, several goals may be considered. 
Please rate how important each of these is, from 1 (unimportant) to 5 (very important).  

This table shows the percentage giving the highest ratings (4-5).
 
`r  propagree(4,df,mycutoff,respmax=5,thisrow,jisccodes)` 
 
 **Free text comments on item 4**    

`r mytext <- df$x10_4b_op; gatherfree(4,mytext)` 

## Factors hindering academic institutions' response to serious research misconduct 
### Item 5: Various factors may hinder academic institutions' response to serious research misconduct. 
Please rate the following from 1 (not much of a hindrance) to 5 (substantial hindrance) 

  
`r  propagree(5,df,mycutoff,respmax=5,thisrow,jisccodes)` 


 **Free text comments on item 5**    

`r mytext <- df$x12_5b_op; gatherfree(5,mytext)` 


## Factors driving serious research misconduct 
### Item 6: What is the impact of these factors in encouraging researchers to commit serious research misconduct? 
Please rate from 1 (little impact) to 5 (large impact) 





`r  propagree(6,df,mycutoff,respmax=5,thisrow,jisccodes)` 

 **Free text comments on item 6**    

`r mytext <- df$x14_6b_op; gatherfree(6,mytext)` 

## Role of post-publication peer review
### Item 7: Please rate the impact of the following from 1 = strongly negative to 5 = strongly positive in drawing attention to serious academic misconduct
Percentage rating 4-5.

`r  propagree(7,df,mycutoff,respmax=5,thisrow,jisccodes)` 


 

 **Free text comments on item 7**    

`r mytext <- df$x16_7b_op; gatherfree(7,mytext)` 


## Reporting serious research misconduct   
### Item 8: Official channels for reporting misconduct seldom work efficiently   
Table shows percentages selecting agree/strongly agree.


`r  propagree(8,df,mycutoff,respmax=5,thisrow,jisccodes)`

 **Free text comments on item 8**    
 

`r mytext <- df$x18_8b_op; gatherfree(8,mytext)` 

## Models for addressing serious research misconduct 
### Item 9: In an ideal world where resources are not an issue, which is the most suitable model/system for addressing serious research misconduct? 
Percentages responding 4-5 (preferred/strongly preferred)  
`r  propagree(9,df,mycutoff,respmax=5,thisrow,jisccodes)` 


 **Free text comments on item 9**    

`r mytext <- df$x20_9b_op; gatherfree(9,mytext)` 

## Role of employers
### Item 10: Prospective employers should undertake rigorous due diligence and, as far as possible, check with previous employers to ask if there have been any investigations into serious research misconduct.  

Response options are mutually exclusive.  
Table shows percentages selecting each option in each group.  
(For personalised reports, * denotes your response).  

`r makecattab(myjisc,10,df,thisrow,myterms<-c('Agree, regardless of outcome of investigation','Agree, but only if investigation found evidence of serious research misconduct','Neutral','Disagree','Strongly disagree'),jisccodes)`



 **Free text comments on item 10**    

`r mytext <- df$x22_10b_o; gatherfree(10,mytext)` 

\pagebreak

### Item 11: Employers, funders and publishers of research should be legally required to share information to support investigations of serious research misconduct.  
Table shows percentage selecting 4-5 (agree/strongly agree) 


`r  propagree(11,df,mycutoff,respmax=5,thisrow,jisccodes)`

 **Free text comments on item 11**    

`r mytext <- df$x24_11b_o; gatherfree(11,mytext)` 

## Solutions to serious research misconduct
### Item 12: Given that we have finite resources, which solutions to serious research misconduct should be prioritised in funding?

Table shows percentage rating 4-5 (i.e. effective/highly effective).
`r  propagree(12,df,mycutoff,respmax=5,thisrow,jisccodes)` 

\pagebreak

 **Free text comments on item 12**    

`r mytext <- df$x26_12b_o; gatherfree(12,mytext)` 
\pagebreak

## Role of publishers  
### Item 13: Publishers and their journal editors are responsible for ensuring the literature is decontaminated from erroneous work promptly. 
Table shows percentage rating 4-5 (i.e. agree/strongly agree) with the subitem.
 

`r  propagree(13,df,mycutoff,respmax=5,thisrow,jisccodes)` 

 **Free text comments on item 13**    

`r mytext <- df$x28_13b_o; gatherfree(13,mytext)`

## Whistleblowers and bystanders  
### Item 14: Please rate your agreement with the following statements about whistleblowers from 1 = strongly disagree to 5 = strongly agree  

Table shows percentage rating 4-5 (agree/strongly agree).

`r  propagree(14,df,mycutoff,respmax=5,thisrow,jisccodes)` 

 **Free text comments on item 14**    

`r mytext <- df$x30_14b_o; gatherfree(14,mytext)`

\pagebreak

## When serious research misconduct is confirmed  
### Item 15: Which of these practices should be options for institutions when serious research misconduct is confirmed?

Table shows percentages responding 4-5 (agree/strongly agree)


`r  propagree(15,df,mycutoff,respmax=5,thisrow,jisccodes)` 

 **Free text comments on item 15**    

`r mytext <- df$x32_15b_o; gatherfree(15,mytext)`

## Unintended consequences/barriers to progress  
### Item 16: Please rate your agreement with the following statements about unintended consequences/barriers to progress
Percentage rating 4-5 (agree/strongly agree)


`r  propagree(16,df,mycutoff,respmax=5,thisrow,jisccodes)` 
\pagebreak
 **Free text comments on item 16**    

`r mytext <- df$x34_16b_o; gatherfree(16,mytext)`

\pagebreak

### Item 17:  How interested would you be in having discussion of the following topics at the in-person meeting in April?  
Percentage rating 4-5 (interested/strongly interested)

N.B. We plan parallel discussion sessions, so a topic does not need strong level of interest from everyone to be included.  


`r  propagree(17,df,mycutoff,respmax=5,thisrow,jisccodes)` 

 **Free text comments on item 17**    

`r mytext <- df$x36_17b_o; gatherfree(17,mytext)`

`r write.csv(reportorder,'reportOrder_round2.csv',row.names=F)`



